The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-11 paper/mri paper.tex
solvability criterion stuff

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.3]{firstorder_velocity.eps}
\caption{First order velocity perturbations. Streamlines represent velocity in the vertical-radial plane, with thicker streamlines corresponding to faster speeds. The colorbar represents azimuthal velocity.}
\end{figure*}

>>>>

To find a bounded solution at each order, we eliminate secular terms -- terms which are resonant with solutions to the homogenous equation, and cause the solution to grow without bound. The elimination of secular terms requires enforcement of solvability criteria, which arise as a consequence of the Fredholm alternative (e.g. Guenther \& Lee 1988). The solvability criterion is found by forcing the inner product of the equation with its adjoint homogenous solution to be zero. For instance, Equation \ref{ordere2} contains a term $\widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}$ that is resonant with $e^{i k_c z}$. Because the adjoint homogenous equation

\beq
\mathcal{L}^\dagger \mathbf{V}^\dagger = 0
\eeq

has a nontrivial solution, the solvability criterion

\beq
\left< \mathbf{V}^\dagger \cdot \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}\right> = 0 
\eeq

must be satisfied in order for Equation \ref{ordere2} to have a solution.

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.3]{firstorder_velocity.eps}
\caption{First order velocity perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to faster speeds. The colorbar represents azimuthal velocity.}
\end{figure*}
